---
title: "R Notebook"
output: html_notebook
---
Importing Packages
```{r}
install.packages("tidytext")
install.packages("tidyverse")
install.packages("sentimentr")
install.packages("textdata")
install.packages("stringi")
```

Importing Libraries
```{r}
library(tidytext)
library(tidyverse)
library(textdata)
library(sentimentr)
library(stringr)
library(stringi)
```
Importing data
```{r}
media_agency_df <- read_csv("data_in/media_agency_tweets.csv")
media_agency_df <- media_agency_df[ , colSums(is.na(media_agency_df)) < nrow(media_agency_df)]

```

Wrangeling data
```{r}
picky_mtdf<- media_tweets_df %>%
  select(screen_name,text) %>%
   unnest_tokens("word", text)

data(stop_words)

picky_mtdf <- picky_mtdf %>%
  anti_join(stop_words)

picky_mtdf%>%
  filter(!(word=="https"|
             word=="rt"|
             word=="t.co"|
             word=="amp")) %>%
  count(word, sort=TRUE)
```

```{r}
set_tweets <- media_tweets_df %>%
  select(text)
set_tweets <- unlist(strsplit(set_tweets, "\\."))
set_tweets[grep(pattern = "Covid-19", text, ignore.case = T)]
filtered_tweets<- media_tweets_df[grep("covid", media_tweets_df$text), ignore.case = TRUE]
```

```{r}
media_tweets_df %>%
  str_extract_all(text, "([:alnum:]+\\s)*Covid-19[[:alnum:]\\s]*\\.")[[1]]
```
Reasons for the media sources chosen:
News 24 : Recognized by APP Annie (App Annie is the standard in app analytics and app market data) as the most known South African internet media source. (Chinese Academy of Cyberspace Studiespublisher=Springer (15 September 2018). World Internet Development Report 2017: Translated by Peng Ping. p. 203. ISBN 9783662575246. OCLC 1052766508.)
Times Live
EWN
eNCA
SABC
Justify why we use these agencies. Size? Reputable? unbias?

